---
title: "FIGI T2D additional analyses"
date: '`r paste("Updated on", Sys.Date())`'
output: 
  html_document:
    #css: posthoc_report.css
    toc: false
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    theme: "paper"
---

<style type="text/css">

/* Whole document: */
body{
  font-family: Helvetica;
  font-size: 12pt;
}
/* Headers */
/* h1,h2,h3,h4,h5,h6{ */
/*  font-size: 18pt; */
}

</style>

Check models with and without adjustment for the following covariates:  
- batch  
- country  
- season of blood draw  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(data.table)
library(stargazer)
library(lmtest)
library(broom)
library(figifs)
library(kableExtra)
```

```{r, include = F}
# FIGI gxe set (gxe == 1, EUR_subset == 1)
figi <- readRDS("/media/work/gwis/results/input/FIGI_v2.3_gxeset_analysis_data_glm.rds")
load("/home/rak/data/FIGI_vitaminD_epi-200527/pooled_vitD_25OH.RData")
load("/home/rak/data/FIGI_vitaminD_epi-200527/vitd_crp_UKB.Rdata")

figiD <- inner_join(figi, vitD, 'pooledcompassid') %>% 
  mutate(group = "others")

# figiD <- inner_join(figi, vitD, 'pooledcompassid') %>% 
#   mutate(group = "others") %>% 
#   filter(vitd25 < 1000)

bio.uk <- mutate(bio.uk, f.eid = as.character(f.eid))
ukb <- filter(figi, study_gxe == "UKB_1")
ukbD <- inner_join(ukb, bio.uk, by = c("compassid" = "f.eid")) %>% 
  mutate(vitd25 = f.30890.0.0, 
         crp = f.30710.0.0, 
         group = 'ukb')

out <- bind_rows(figiD[, c('pooledcompassid', 'group', 'vitd25', 'studyname')], 
                 ukbD[, c('pooledcompassid', 'group', 'vitd25', 'studyname')]) %>% 
  mutate(group = as.factor(group)) 

out_mean <- out %>% 
  group_by(group) %>%
  dplyr::summarize(group.mean = mean(vitd25, na.rm = T))
```

## WHI blood draw batch

WHI has 'batch' information which correspond to multiple ancillary studies.  

Table:
``` {r}
whi <- filter(figiD, grepl("WHI", study.x)) %>% 
  mutate(batch = as.factor(whi_testver))

table(whi$batch, whi$outcome)
```

Models: 
```{r, results = 'asis'}
model1 <- glm(outcome ~ vitd25 + age_ref_imp + pc1 + pc2 + pc3,         data = whi, family = 'binomial')
model2 <- glm(outcome ~ vitd25 + age_ref_imp + pc1 + pc2 + pc3 + batch, data = whi, family = 'binomial')

stargazer(model1, model2, 
          type = 'html', 
          apply.coef = exp, 
          ci = T, 
          omit = c("pc"), 
          column.labels = c("baseline", "adjust by batch"))
```


## EPIC

Country varible adjustment
```{r}
# Create country variable
spain <- c("Asturias", "Granada", "Murcia", "Navarra", "San Sebastian")
netherlands <- c("Bilthoven", "Utrecht")
uk <- c("Cambridge", "UK General Population", "UK Health Conscious")
italy <- c("Florence", "Naples", "Turin", "Varese")
greece <- c("Greece")
germany <- c("Heidelberg", "Potsdam")
france <- c("Northeast France", "Northwest France", "South coast France", "South France")
croatia <- c("Ragusa")
switzerland <- c("Umea")

epic <- filter(figiD, grepl("EPIC", study_gxe )) %>% 
  mutate(study_country = case_when(study_site %in% spain ~ "Spain", 
                                   study_site %in% netherlands ~ "Netherlands", 
                                   study_site %in% uk ~ "UK", 
                                   study_site %in% italy ~ "Italy", 
                                   study_site %in% greece ~ "Greece", 
                                   study_site %in% germany ~ "Germany", 
                                   study_site %in% france ~ "France", 
                                   study_site %in% croatia ~ "Croatia", 
                                   study_site %in% switzerland ~ "Switzerland"),
         study_country = as.factor(study_country))
```

Table:
```{r}
table(epic$study_country, epic$outcome)
```

Models:
```{r, results = 'asis'}
model1 <- glm(outcome ~ vitd25 + age_ref_imp + sex + pc1 + pc2 + pc3,                 data = epic, family = 'binomial')
model2 <- glm(outcome ~ vitd25 + age_ref_imp + sex + pc1 + pc2 + pc3 + study_country, data = epic, family = 'binomial')

stargazer(model1, model2, type = 'html', apply.coef = exp, ci = T, omit = c("pc"), column.labels = c("baseline", "country adj."))
```


## Blood draw month/season

Blood draw month available for NHS and WHI: 
```{r}
table(vitD$blood_month, vitD$study)
```

UKB has 'assay date', but this seems to correspond to date the assay was carried rather than when blood sample was drawn (confirm). Is there a variable that captures blood draw date in UKB data? I see "Date of attending assessment centre" in data dictionary? 


# Models - subset of studies with blood month available
```{r, results = 'asis'}

nhs_whi <- figiD %>% 
  dplyr::filter(study.x %in% c("NHS", "WHI"))

model1 <- glm(outcome ~ vitd25 + age_ref_imp + sex + pc1 + pc2 + pc3 + study.x,               data = nhs_whi, family = 'binomial')
model2 <- glm(outcome ~ vitd25 + age_ref_imp + sex + pc1 + pc2 + pc3 + study.x + blood_month, data = nhs_whi, family = 'binomial')

stargazer(model1, model2, type = 'html', apply.coef = exp, ci = T, omit = c("pc"), column.labels = c("baseline", "blood month"))
```