---
title: "pure HRT variable creation and summary"
output: html_document
theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = F}
library(tidyverse)
library(data.table)
library(lmtest)
library(expss)
library(glue)

# figi_gxe <- readRDS("/media/work/gwis/results/input/FIGI_v2.3_gxeset_analysis_data_glm.rds")
figi_gxe <- readRDS("/media/work/gwis/data/FIGI_EpiData/FIGI_v2.3_gxeset_analysis_data_glm.rds")
snps <- readRDS("/media/work/gwis/posthoc/gwis_sig_results_output_ep_ref_pm_gxe.rds")
figi_gxe_snp <- inner_join(figi_gxe, snps, 'vcfid')
# snp <- "X1.53785007.C.T_dose"

# original ep_ref_pm_gxe
ep_ref_pm_gxe <- readRDS("/media/work/gwis/results/input/FIGI_v2.3_gxeset_ep_ref_pm_gxe_basic_covars_glm.rds") %>% 
  rename_all(tolower) %>% 
  inner_join(snps, 'vcfid')
eo_ref_pm_gxe <- readRDS("/media/work/gwis/results/input/FIGI_v2.3_gxeset_eo_ref_pm_gxe_basic_covars_glm.rds") %>% 
   rename_all(tolower) %>% 
  inner_join(snps, 'vcfid')
```


Variable summary from Yi:

From Yi and Yu:

| Ever                   | Description                                                             |
|------------------------|-------------------------------------------------------------------------|
| hrt_ref_pm2No          | 1= no EO and no EP and no any HRT; 0= any EO,EP,any HRT                 |
| pure_eo_allNo          | 1= no EO and no EP and no any HRT; 0= pure EO and no EP and no any HRT  |
| pure_eo_anyNo          | 1= no EO or  no EP or  no any HRT; 0 = pure EO and no EP and no any HRT |
| pure_ep_allNo          | 1= no EO and no EP and no any HRT; 0 = pure EP and no EO and no any HRT |
| pure_ep_anyNo          | 1= no EO or  no EP or  no any HRT; 0 = pure EP and no EO and no any HRT |
| eo_allNo               | 1= no EO and no EP and no any HRT;0 =  EO regardless  EP/any HRT        |
| eo_anyNo               | 1= no EO or  no EP or  no any HRT; 0 =  EO regardless  EP/any HRT       |
| ep_allNo               | 1= no EO and no EP and no any HRT; 0 =  EP regardless  EP/any HRT       |
| ep_anyNo               | 1= no EO or  no EP or  no any HRT; 0 = EP regardless  EP/any HRT        |
| eo_ref_pm              | Post menopausal EO use                                                  |
| ep_ref_pm              | Post menopausal EP use                                                  |
| horm_ref_pm            | Post menopausal any hormone use                                         |
| hrt_ref_pm2            | 0= no EO and no EP and no any HRT; 1= any EO,EP,any HRT                 |
| pure_eo_all            | 0= no EO and no EP and no any HRT; 1 = pure EO and no EP and no any HRT |
| pure_ep_all            | 0= no EO and no EP and no any HRT; 1 = pure EO and no EP and no any HRT |
| eo_all (eo_ref_pm_gxe) | 0= no EO and no EP and no any HRT;1 =  EO regardless  EP/any HRT        |
| ep_all (ep_ref_pm_gxe) | 0= no EO and no EP and no any HRT; 1 =  EP regardless  EP/any HRT       |



Request from Yu:

> I would like to request for re-analyzing GxE based on pure definition for EO and EP? Because we have found a significant SNP (rs79439591) by EP but neither SNPs in LD with it nor functional annotation, I guess the SNP could be gone if we use stringent EP definition. You could only check for this SNP first, don’t have to run analysis for all.   


<br> 

----

<br>


# recode variables and calculate associations

## E+P

### ep_ref_pm == "Yes"
```{r}
ep_yes <- filter(figi_gxe, ep_ref_pm == "Yes")
cro(ep_yes$eo_ref_pm, ep_yes$hrt_ref_pm2)
```

### ep_ref_pm == "No"
```{r}
ep_no <- filter(figi_gxe, ep_ref_pm == "No")
cro(ep_no$eo_ref_pm, ep_no$hrt_ref_pm2)
```


`ep_ref_pm_gxe` includes individuals that were treated with ONLY ESTROGEN. Exclude from definition to create `pure_ep_allNo`: 

### pure_ep_allNo:
```{r}
tmp <- figi_gxe %>% 
  mutate(pure_ep_allNo = ifelse(ep_ref_pm == "Yes" & eo_ref_pm == "No", "Yes",
                       ifelse(ep_ref_pm == "No" & hrt_ref_pm2 == "No" & eo_ref_pm == "No", "No", NA)))

cro(tmp$study_gxe, tmp$pure_ep_allNo)
```

Remove studies that only have either 0 or 1 pure_ep_allNo value or very sparse cells e.g. CLUEII. While this isn't necessary for GLM, I do it for GxEScanR so let me keep things consistent just in case:
```{r}
drops <- data.frame(table(tmp$outcome, tmp[, 'pure_ep_allNo'], tmp$study_gxe)) %>% 
  filter(Freq <= 0)
figi_gxe_pure_ep <- tmp %>% 
  filter(!study_gxe %in% unique(drops$Var3)) %>% 
  dplyr::mutate(study_gxe = fct_drop(study_gxe)) %>% 
  dplyr::select(vcfid, outcome, age_ref_imp, sex, study_gxe, pure_ep_allNo, pc1, pc2, pc3) %>% 
  filter(complete.cases(.))


cro(figi_gxe_pure_ep$study_gxe, figi_gxe_pure_ep$pure_ep_allNo)
```





<br>

----

<br>






## E only

### eo_ref_pm == "Yes"
```{r}
eo_yes <- filter(figi_gxe, eo_ref_pm == "Yes")
cro(eo_yes$ep_ref_pm, eo_yes$hrt_ref_pm2)
```

### eo_ref_pm == "No"
```{r}
eo_no <- filter(figi_gxe, eo_ref_pm == "No")
cro(eo_no$ep_ref_pm, eo_no$hrt_ref_pm2)
```


similar to estrogen+progesterone variable, `eo_ref_pm_gxe` includes individuals that were treated with E+P. Exclude from definition to create `pure_eo_allNo`: 

### pure_eo_allNo:
```{r}
tmp <- figi_gxe %>% 
  mutate(pure_eo_allNo = ifelse(eo_ref_pm == "Yes" & ep_ref_pm == "No", "Yes",
                       ifelse(eo_ref_pm == "No" & hrt_ref_pm2 == "No" & ep_ref_pm == "No", "No", NA)))

cro(tmp$study_gxe, tmp$pure_eo_allNo)
```

Again, remove studies that only have either 0 or 1 pure_eo_allNo value or very sparse cells:
```{r}
drops <- data.frame(table(tmp$outcome, tmp[, 'pure_eo_allNo'], tmp$study_gxe)) %>% 
  filter(Freq <= 0)
figi_gxe_pure_eo <- tmp %>% 
  filter(!study_gxe %in% unique(drops$Var3)) %>% 
  dplyr::mutate(study_gxe = fct_drop(study_gxe)) %>% 
  dplyr::select(vcfid, outcome, age_ref_imp, sex, study_gxe, pure_eo_allNo, pc1, pc2, pc3) %>% 
  filter(complete.cases(.))

cro(figi_gxe_pure_eo$study_gxe, figi_gxe_pure_eo$pure_eo_allNo)
```



<br>

----

<br>

# Association with rs79439591 (1:53785007:C:T)


## start with `pure_ep_allNo`
```{r}
exposure <- "pure_ep_allNo"
snp <- "X1.53785007.C.T_dose"

dat <- inner_join(figi_gxe_pure_ep, snps, 'vcfid')

model     <- glm(glue("outcome ~ {exposure}*{snp} + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = dat, family = 'binomial')
model_ref <- glm(glue("outcome ~ {exposure}+{snp} + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = dat, family = 'binomial')
summary(model)
lrtest(model, model_ref)


# original ep_ref_pm_gxe variable:
exposure <- "ep_ref_pm_gxe"

model     <- glm(glue("outcome ~ {exposure}*{snp} + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = ep_ref_pm_gxe, family = 'binomial')
model_ref <- glm(glue("outcome ~ {exposure}+{snp} + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = ep_ref_pm_gxe, family = 'binomial')
summary(model)
lrtest(model, model_ref)

```


<br> 

---- 

<br> 


## `pure_ep_allNo` - 2DF results
```{r}
exposure <- "pure_ep_allNo"
snp <- "X1.53785007.C.T_dose"

dat <- inner_join(figi_gxe_pure_ep, snps, 'vcfid')

model     <- glm(glue("outcome ~ {exposure}*{snp} + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = dat, family = 'binomial')
model_ref <- glm(glue("outcome ~ {exposure}       + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = dat, family = 'binomial')
summary(model)
lrtest(model, model_ref)


# original ep_ref_pm_gxe variable:
exposure <- "ep_ref_pm_gxe"

model     <- glm(glue("outcome ~ {exposure}*{snp} + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = ep_ref_pm_gxe, family = 'binomial')
model_ref <- glm(glue("outcome ~ {exposure}       + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = ep_ref_pm_gxe, family = 'binomial')
summary(model)
lrtest(model, model_ref)

```



<br> 

---- 

<br> 



## `pure_ep_allNo` - 3DF results

The more straightforward way to do this would be to reparameterize the model so that you can test all 3 components jointly (D|G, GxE, and E|G -- see Gauderman 2019). However, the way GxEScanR does it is to calculate 2DF and E|G separately, and then adding the chi-square statistics to calculate the p-value. So this is what I'll do here: 


```{r}
exposure <- "pure_ep_allNo"
snp <- "X1.53785007.C.T_dose"

dat <- inner_join(figi_gxe_pure_ep, snps, 'vcfid') %>% 
  mutate(pure_ep_allNo = ifelse(pure_ep_allNo == "Yes", 1, 0))


# GxE chi-square statistic
model     <- glm(glue("outcome ~ {exposure}*{snp} + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = dat, family = 'binomial')
model_ref <- glm(glue("outcome ~ {exposure}       + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = dat, family = 'binomial')
summary(model)
lrtest(model, model_ref) 

chisq_2df = 32.063

# E|G chi-square statistic
model     <- glm(glue("{exposure} ~ {snp} + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = dat, family = 'binomial')
model_ref <- glm(glue("{exposure} ~       + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = dat, family = 'binomial')
summary(model)
lrtest(model, model_ref)

chisq_eg = 0.3319

chisq_3df = chisq_2df + chisq_eg

# 3DF P-VALUE: 
pchisq(chisq_3df, lower.tail = F, df = 3)


```


<br> 

---- 

<br> 



## Question about two-step .. 

To interpret this finding, need to put in context of two-step approach. This is the marginal association for this SNP, keeping in mind that it's adjusted by the exposure variable:

```{r}
# pure EP
exposure <- "pure_ep_allNo"
snp <- "X1.53785007.C.T_dose"

dat <- inner_join(figi_gxe_pure_ep, snps, 'vcfid')

model     <- glm(glue("outcome ~ {exposure} + {snp} + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = dat, family = 'binomial')
model_ref <- glm(glue("outcome ~ {exposure}         + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = dat, family = 'binomial')
summary(model)
lrtest(model, model_ref)


# original ep_ref_pm_gxe variable
exposure <- "ep_ref_pm_gxe"

model     <- glm(glue("outcome ~ {exposure} + {snp} + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = ep_ref_pm_gxe, family = 'binomial')
model_ref <- glm(glue("outcome ~ {exposure}         + age_ref_imp + pc1 + pc2 + pc3 + study_gxe"), data = ep_ref_pm_gxe, family = 'binomial')
summary(model)
lrtest(model, model_ref)
```

I'm not sure if this SNP would be significant because assignment to the first Bin depends on the other SNPs with high D|G associations. I need to investigate all the SNPs in the first few bins to be sure. But for now, can say that D|G and GxE statistics are slight attenutated using the pure EP definition.  