---
date: '`r paste("Updated on", Sys.Date())`'
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    theme: "united"
params:
  exposure: "pure_ep_allNo"
  hrc_version: "v2.3"
  covariates: !r c("age_ref_imp", "pc1", "pc2", "pc3", "study_gxe")
title: "FIGI GWIS Results - `r params$exposure`"
---


```{r setup, include=F}
knitr::opts_chunk$set(echo = F, message = F, warning = F, error = F)

library(tidyverse)
library(data.table)
library(ggplot2)
library(qqman)
library(table1)
library(meta)
library(rlang)
library(broom)
library(effects)
library(figifs)
library(DT)
library(grid)
library(sjPlot)
library(stargazer)
library(nnet)
library(forcats)
library(kableExtra)
library(reticulate)
library(glue)

# source of meta/pooled analysis results
output_dir = paste0("/media/work/gwis/posthoc/", params$exposure, "/")
```

<style type="text/css">
.main-container {
  max-width: 1800px !important;
  margin-left: auto;
  margin-right: auto;
}

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  margin-top: 1em;
  margin-bottom: 1em;
}

/* Whole document: */
body{
  font-family: Helvetica;
  font-size: 14pt;
}
/* Headers */
/* h1,h2,h3,h4,h5,h6{ */
/*  font-size: 24pt; */
}

</style>

<!-- # Updates -->
<!-- ```{r child = paste0("results_report_child_updates.Rmd")} -->
<!-- ``` -->

<br>

---

<br>

# ``r params$exposure`` Main Effects

## Description
- Box/bar plots
- Descriptive statistics by outcome and exposure status (when applicable) for CRC related variables. Only includes subset of samples with available ``r params$exposure`` information
- Meta-analysis of CRC/``r params$exposure`` association. Results are presented overall and stratified by sex, tumor site, and relevant covariates
- Pooled analysis of CRC/``r params$exposure`` in pooled FIGI GxE subset. Results also presented overall and stratified. Adjustment covariates same as those for meta-analyses, in addition to study_gxe

<br>

---

<br>

```{r child = paste0("results_descriptive_ver2.Rmd")}
```

## Results

Adjusted by age and sex (energy, study/platform, PCs when applicable)  

### Meta analysis {.tabset}
```{r child = 'results_meta.Rmd'}
```

### Pooled analysis {.tabset}
```{r child = 'results_pooled.Rmd'}
```

