---
title: "FIGI PhysAct sensitivity analyses"
author: "AK"
date:  "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)
library(glue)
library(broom)
library(meta)
library(kableExtra)
```

## Summary of main findings for physact followup


variable          finding           method
---------------   ---------------   ---------
active_met_875    15:32994756:T:C   gao 99.5
active_met_1800   15:33008870:T:C   gao 97.5
methrswklnsqc2    20:49693755:T:C   GxE
methrswklns       21:44227260:T:C   case-only*


## Sensivity analyses

#### Covariate adjustment
I ran 5 different covariate sets:     
- set1: age, sex, energy, pc, study     
- set2: set1 + bmi + smk_ever   
- set3: set1 + famhx  
- set4: set1 + bmi + smk_ever + famhx  
- set5: set4 + height10 + redmeat + procmeat + folatetot + fiber + fruit + vegetable + calciumtot + NSAIDs + alcoholc (3 categories)  

https://drive.google.com/open?id=1szTGSDsu5bDVkS18MJEFWSfwBzvOiE_Q&authuser=andreeki%40usc.edu&usp=drive_fs

<br>

#### Repeat sensitivity analysis, exclude WHI_2, WHI_3 (e.g. clinical trials after review of study background)
https://drive.google.com/open?id=1tC7p3rkeCq1pep_nEArhTTgEG2VqZC09&authuser=andreeki%40usc.edu&usp=drive_fs

<br>

#### Repeat sensitivity analyses, exclude WHI_2, WHI3 + studies that are primarily composed of adenoma cases (HPFS, NHS -- see email)

https://drive.google.com/open?id=1tLab-trZGJA3jSW2TMMU0tL8PICGi-2A&authuser=andreeki%40usc.edu&usp=drive_fs



## active_met_875 by study


#### simple tabulation
```{r}

x <- readRDS("/media/work/gwis_test/active_met_875/data/tmp.rds")
# table(x$study_gxe, x$active_met_875)


out <- x %>% 
  group_by(study_gxe, active_met_875, outcome) %>% 
  summarise(N = n()) %>% 
  pivot_wider(names_from = outcome, values_from = N) %>% 
  ungroup() %>% 
  group_by(study_gxe) %>% 
  mutate(pct0 = round((`0` / sum(`0`)*100), 1), 
         pct1 = round((`1` / sum(`1`)*100), 1), 
         control = paste0(`0`, " (", pct0, ")"), 
         case = paste0(`1`, " (", pct1, ")")) %>% 
  dplyr::select(study_gxe, active_met_875, control, case)


# chisq pvalues
chisq.pvalues <- x %>% 
  group_by(study_gxe, active_met_875, outcome) %>% 
  summarise(N = n()) %>% 
  # pivot_wider(names_from = outcome, values_from = N, names_prefix = "stat") %>% 
  ungroup() %>% dplyr::select(-active_met_875, -outcome) %>%
  group_by(study_gxe) %>% 
  summarise(pval = round(chisq.test(matrix(N, ncol = 2))$p.value, 3)) %>%
  pull(pval)
  
tmp <- rep("", 27)
tmp2 <- as.vector(rbind(tmp, chisq.pvalues))

out$chisq_pvalue = tmp2

kable(out) %>% 
  kable_paper()

```
